### 2022-09-19 chapters/programming_languages/programming_languages.tex
Proofreading

As we saw in the last chapter, one of the most important things about a test is how well it \textsc{represents} the production environment.
Therefore, we extend this study to include real-world use cases, with two case studies provided in the parts that follow.

\section{Investigating Remote Procedure Call Frameworks}
\import{\currfiledir/rpc}{rpc}
\clearpage

>>>>

As we saw in the previous chapter, one of the most important things about a benchmark is how well it \textsc{reflects} the production environment.
Therefore, we extend our study to cover real-world use cases, including two case studies reported in the following sections.

\section{Investigating Remote Procedure Call Frameworks}
\import{\currfiledir/rpc}{rpc}
% \clearpage
